---
title: "Spiritual epidemiology ANALYSIS (KW first pass)"
subtitle: "Last updated: 2019-04-18"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

This is Kara's first pass at analyzing the Spiritual Epidemiology data (with data from 2019-03-08). (Note: PDF printed portrait, 80% zoom, minimum margins.)

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 4, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
library(tidyverse)
library(langcog)
library(psych)
library(readxl)
library(cowplot)
library(lme4)
library(lmerTest)
library(kableExtra)
library(lubridate)

theme_set(theme_bw())
```


```{r}
d_por <- read.csv("./data_wrangled/d_por.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))

d_por_scored <- read.csv("./data_wrangled/d_por_scored.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))
```

```{r}
d_spex_base_q2to23 <- read.csv("./data_wrangled/d_spex_base_q2to23.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))

d_spex_base_q2to23_scored_propall <- read.csv("./data_wrangled/d_spex_base_q2to23_scored_propall.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))

d_spex_base_q2to23_scored_first5 <- read.csv("./data_wrangled/d_spex_base_q2to23_scored_first5.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))
```

```{r}
d_spex_base_q2to10 <- read.csv("./data_wrangled/d_spex_base_q2to10.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))

d_spex_base_q2to10_scored <- read.csv("./data_wrangled/d_spex_base_q2to10_scored.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))
```

```{r}
d_spex_base_q11to15 <- read.csv("data_wrangled/d_spex_base_q11to15.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))

d_spex_base_q11to15_scored <- read.csv("data_wrangled/d_spex_base_q11to15_scored.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))
```

```{r}
d_spex_base_q16to21 <- read.csv("data_wrangled/d_spex_base_q16to21.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))

d_spex_base_q16to21_scored <- read.csv("data_wrangled/d_spex_base_q16to21_scored.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))
```

```{r}
d_spex_base_q22to23 <- read.csv("data_wrangled/d_spex_base_q22to23.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))

d_spex_base_q22to23_scored <- read.csv("data_wrangled/d_spex_base_q22to23_scored.csv", row.names = "X") %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))
```

```{r}
# alternative contrasts for site
contrasts_ctry_eff <- cbind("US" = c(1, 0, 0, 0, -1),
                            "GH" = c(0, 1, 0, 0, -1),
                            "TH" = c(0, 0, 1, 0, -1),
                            "CH" = c(0, 0, 0, 1, -1))

contrasts_ctry_dum <- cbind("GH_US" = c(0, 1, 0, 0, 0),
                            "TH_US" = c(0, 0, 1, 0, 0),
                            "CH_US" = c(0, 0, 0, 1, 0),
                            "VT_US" = c(0, 0, 0, 0, 1))

contrasts_ctry_ctr <- cbind("nonUS_US" = c(-4, 1, 1, 1, 1),
                            "GHVT_THCH" = c(0, 1, -1, -1, 1),
                            "GH_VT" = c(0, 1, 0, 0, -1),
                            "TH_CH" = c(0, 0, 1, -1, 0))
```

# Porosity

## Overall scores

```{r}
d_por_scored_mb <- d_por_scored %>%
  group_by(epi_ctry) %>%
  multi_boot_standard("score") %>%
  ungroup() %>%
  mutate(epi_ctry = factor(epi_ctry, levels = c("US", "Ghana", "Thailand", 
                                                "China", "Vanuatu")))

# effect-code by default
contrasts(d_por_scored$epi_ctry) <- contr.sum(5)
```

```{r, fig.width = 4, fig.asp = 0.6, include = T}
por_plot_a <- ggplot(d_por_scored,
                     aes(x = epi_ctry, y = score, color = epi_ctry)) +
  geom_hline(yintercept = 0*16, lty = 2, color = "black") +
  geom_hline(yintercept = 0.5*16, lty = 2, color = "black") +
  geom_hline(yintercept = 1*16, lty = 2, color = "black") +
  geom_jitter(height = 0, width = 0.4, alpha = 0.2, show.legend = F) +
  geom_pointrange(data = d_por_scored_mb,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black", fatten = 2) +
  geom_text(data = data.frame(x = 0.5,
                              y = c(0*16, 0.5*16, 1*16),
                              lab = c("~ All answers 'no'",
                                      "", 
                                      # "~ All answers 'maybe'",
                                      "~ All answers 'yes'")),
            aes(x = x, y = y, label = lab),
            color = "black", hjust = 0, nudge_y = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 16, 4)) +
  # ylim(0, 16) +
  labs(title = "Porosity by site",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", y = "Porosity score (average response, range: 0-16)")

por_plot_b <- ggplot(d_por_scored_mb,
                     aes(x = epi_ctry, color = epi_ctry)) +
  # geom_hline(yintercept = 0*16, lty = 2, color = "black") +
  geom_hline(yintercept = 0.5*16, lty = 2, color = "black") +
  # geom_hline(yintercept = 1*16, lty = 2, color = "black") +
  geom_pointrange(aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 4, show.legend = F) +
  # geom_text(data = data.frame(x = 0.5,
  #                             y = 0.5 * 16, # c(0*16, 0.5*16, 1*16),
  #                             lab = "~ All answers 'maybe'"),
  #                                   # c("~ All answers 'no'",
  #                                   #   "~ All answers 'maybe'",
  #                                   #   "~ All answers 'yes'")),
  #           aes(x = x, y = y, label = lab), 
  #           color = "black", hjust = 0, nudge_y = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 16, 4)) +
  labs(title = "Porosity by site (zoomed in)",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", y = "Porosity score (average response, range: 0-16)")

plot_grid(por_plot_a, por_plot_b, ncol = 2)
```

```{r}
r_por <- lm(score ~ epi_ctry, d_por_scored,
            contrasts = list(epi_ctry = contrasts_ctry_ctr))
```

```{r, include = T}
summary(r_por)$coefficients %>%
  data.frame() %>%
  rownames_to_column("parameter") %>%
  rename(b = Estimate, `standard error` = Std..Error, `t` = t.value,
         p = Pr...t..) %>%
  mutate_at(vars(-parameter, -p), funs(round(., 2))) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round(p, 3)),
         significant = ifelse(p < 0.05, "*", "")) %>%
  kable(align = c("l", rep("r", 5), "l")) %>%
  kable_styling() %>%
  row_spec(c(2:5), bold = T)
```

<P style="page-break-before: always">
## By item

```{r, fig.width = 6, fig.asp = 1, include = T}
d_por %>%
  filter(!grepl("a", question), !grepl("b", question), 
         !grepl("c", question)) %>%
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  ggplot(aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  facet_wrap(~ reorder(str_wrap(question_text, 50), order), ncol = 4) +
  geom_jitter(data = d_por %>% 
                filter(!grepl("a", question), !grepl("b", question), 
                       !grepl("c", question)), aes(y = response), 
              height = 0.05, alpha = 0.08, show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.5), 
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "Porosity scale: Responses to individual items",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", 
       y = "Mean response (0 = it does not happen, 0.5 = it might happen, 1 = it definitely happens")
```

```{r}
por_fu_question_text <- d_por %>%
  filter(question %in% c("epi_1_01", "epi_1_04", "epi_1_06", "epi_1_07",
                         "epi_1_11", "epi_1_14")) %>%
  distinct(question, question_text, order) %>%
  mutate(question_text = as.character(question_text))
```

```{r, fig.width = 6, fig.asp = 0.8, include = T}
d_por %>%
  filter(grepl("a", question) | grepl("b", question) | grepl("c", question)) %>%
  filter(!grepl("usa", question), !grepl("gha", question), 
         !grepl("chn", question), !grepl("vut", question),
         !grepl("thl", question)) %>% 
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  ggplot(aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  facet_wrap(~ reorder(str_wrap(question_text, 30), order), ncol = 6) +
  geom_jitter(data = d_por %>% 
                filter(grepl("a", question) | grepl("b", question) |
                         grepl("c", question)) %>%
                filter(!grepl("usa", question), !grepl("gha", question), 
                       !grepl("chn", question), !grepl("vut", question),
                       !grepl("thl", question)), aes(y = response), 
              height = 0.05, alpha = 0.08, show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.5), 
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 2, 0.5)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "Porosity scale: Responses to follow-up questions",
       subtitle = paste0(por_fu_question_text$question_text %>% paste0(collapse = '\n'), "\n\nNote: these questions are NOT currently included in Porosity 'scores'\nError bars are bootstrapped 95% CIs"),
       x = "Site", 
       y = "Mean response (0 = no, 1 = a little, 2 = a lot)")
```

```{r}
por_sitespec_question_text <- d_por %>%
  filter(grepl("usa", question) | grepl("gha", question) |
         grepl("chn", question)| grepl("vut", question) |
         grepl("thl", question)) %>%
  distinct(question, question_text, order) %>%
  mutate(question_text = as.character(question_text))
```

```{r, fig.width = 6, fig.asp = 0.4, include = T}
d_por %>%
  filter(grepl("usa", question) | grepl("gha", question) |
         grepl("chn", question)| grepl("vut", question) |
         grepl("thl", question)) %>% 
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  ggplot(aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  facet_wrap(~ reorder(str_wrap(question_text, 40), order), 
             ncol = 4, scales = "free_x") +
  geom_jitter(data = d_por %>% 
                filter(grepl("usa", question) | grepl("gha", question) |
                         grepl("chn", question)| grepl("vut", question) |
                         grepl("thl", question)), aes(y = response), 
              height = 0.05, alpha = 0.08, show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.5), 
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "Porosity scale: Responses to site-specific questions",
       subtitle = "Note: these questions are NOT currently included in Porosity 'scores'\nError bars are bootstrapped 95% CIs",
       x = "Site", 
       y = "Mean response (0 = no, 0.5 = maybe, 1 = yes)")
```

<P style="page-break-before: always">
# All spiritual experiences (Questions #2-23)

## Considering all "beings"

```{r}
d_spex_base_q2to23_scored_propall_mb <- d_spex_base_q2to23_scored_propall %>%
  group_by(epi_ctry) %>%
  multi_boot_standard("score") %>%
  ungroup()
```

```{r, fig.width = 4, fig.asp = 0.6, include = T}
spex_q2to23_plot_a <- ggplot(d_spex_base_q2to23_scored_propall,
                            aes(x = epi_ctry, y = score, 
                                color = epi_ctry)) +
  geom_hline(yintercept = 0*1, lty = 2, color = "black") +
  geom_hline(yintercept = 0.5*1, lty = 2, color = "black") +
  geom_hline(yintercept = 1*1, lty = 2, color = "black") +
  geom_jitter(height = 0, width = 0.4, alpha = 0.2, show.legend = F) +
  geom_pointrange(data = d_spex_base_q2to23_scored_propall_mb,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 2, color = "black", show.legend = F) +
  geom_text(data = data.frame(x = 0.5,
                              y = c(0*1, 0.5*1, 1*1),
                              lab = c("~ All answers 'no'",
                                      "",
                                      # "~ All answers 'maybe'",
                                      "~ All answers 'yes'")),
            aes(x = x, y = y, label = lab),
            color = "black", hjust = 0, nudge_y = 0.05) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  labs(title = "Spiritual experiences (Questions #2-23)",
       subtitle = "Includes all beings for Thailand\nError bars are bootstrapped 95% CIs",
       x = "Site", y = "Proportion score (range: 0-1)")

spex_q2to23_plot_b <- ggplot(d_spex_base_q2to23_scored_propall_mb,
                            aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  fatten = 4, show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  labs(title = "Spiritual experiences (zoomed in)",
       subtitle = "Includes all beings for Thailand\nError bars are bootstrapped 95% CIs",
       x = "Site", y = "Proportion score (range: 0-1)")

plot_grid(spex_q2to23_plot_a, spex_q2to23_plot_b, ncol = 2)
```

```{r}
r_q2to23_scored_propall <- lm(score ~ epi_ctry, 
                              d_spex_base_q2to23_scored_propall,
                              contrasts = list(epi_ctry = contrasts_ctry_ctr))
```

```{r, include = T}
summary(r_q2to23_scored_propall)$coefficients %>%
  data.frame() %>%
  rownames_to_column("parameter") %>%
  rename(b = Estimate, `standard error` = Std..Error, `t` = t.value,
         p = Pr...t..) %>%
  mutate_at(vars(-parameter, -p), funs(round(., 2))) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round(p, 3)),
         significant = ifelse(p < 0.05, "*", "")) %>%
  kable(align = c("l", rep("r", 5), "l")) %>%
  kable_styling() %>%
  row_spec(c(2:5), bold = T)
```

```{r}
r_q2to23_propall <- lmer(response ~ epi_ctry + (1 | epi_subj),
                         d_spex_base_q2to23,
                         contrasts = list(epi_ctry = contrasts_ctry_ctr))
```

```{r, include = F}
summary(r_q2to23_propall)$coefficients %>%
  data.frame() %>%
  rownames_to_column("parameter") %>%
  rename(b = Estimate, `standard error` = Std..Error, `t` = t.value,
         p = Pr...t..) %>%
  mutate_at(vars(-parameter, -p), funs(round(., 2))) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round(p, 3)),
         significant = ifelse(p < 0.05, "*", "")) %>%
  kable(align = c("l", rep("r", 5), "l")) %>%
  kable_styling() %>%
  row_spec(c(2:5), bold = T)
```

<P style="page-break-before: always">
## Considering first five "beings" only

```{r}
d_spex_base_q2to23_scored_first5_mb <- d_spex_base_q2to23_scored_first5 %>%
  group_by(epi_ctry) %>%
  multi_boot_standard("score") %>%
  ungroup()
```

```{r, fig.width = 4, fig.asp = 0.6, include = T}
spex_q2to23_plot_c <- ggplot(d_spex_base_q2to23_scored_first5,
                            aes(x = epi_ctry, y = score, 
                                color = epi_ctry)) +
  geom_hline(yintercept = 0*22, lty = 2, color = "black") +
  geom_hline(yintercept = 0.5*22, lty = 2, color = "black") +
  geom_hline(yintercept = 1*22, lty = 2, color = "black") +
  geom_jitter(height = 0, width = 0.4, alpha = 0.2, show.legend = F) +
  geom_pointrange(data = d_spex_base_q2to23_scored_first5_mb,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 2, color = "black", show.legend = F) +
  geom_text(data = data.frame(x = 0.5,
                              y = c(0*22, 0.5*22, 1*22),
                              lab = c("~ All answers 'no'",
                                      "",
                                      # "~ All answers 'maybe'",
                                      "~ All answers 'yes'")),
            aes(x = x, y = y, label = lab),
            color = "black", hjust = 0, nudge_y = 1) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 22, 2)) +
  labs(title = "Spiritual experiences (Questions #2-23)",
       subtitle = "Includes first five beings for all sites\nError bars are bootstrapped 95% CIs",
       x = "Site", y = "Sum score (range: 0-22)")

spex_q2to23_plot_d <- ggplot(d_spex_base_q2to23_scored_first5_mb,
                            aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  fatten = 4, show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 22, 2)) +
  labs(title = "Spiritual experiences (zoomed in)",
       subtitle = "Includes first five beings for all sites\nError bars are bootstrapped 95% CIs",
       x = "Site", y = "Sum score (range: 0-22)")

plot_grid(spex_q2to23_plot_c, spex_q2to23_plot_d, ncol = 2)
```

```{r}
r_q2to23_scored_first52 <- lm(response ~ epi_ctry, 
                              d_spex_base_q2to23 %>%
                                filter(!question %in% 
                                         c("epi_2_thl12e", "epi_2_thl12f", 
                                           "epi_2_thl12g", "epi_2_thl12h", 
                                           "epi_2_thl12i", "epi_2_thl12j",
                                           "epi_2_thl12k")),
                              contrasts = list(epi_ctry = contrasts_ctry_ctr))
```

```{r, include = T}
summary(r_q2to23_scored_first52)$coefficients %>%
  data.frame() %>%
  rownames_to_column("parameter") %>%
  rename(b = Estimate, `standard error` = Std..Error, `t` = t.value,
         p = Pr...t..) %>%
  mutate_at(vars(-parameter, -p), funs(round(., 2))) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round(p, 3)),
         significant = ifelse(p < 0.05, "*", "")) %>%
  kable(align = c("l", rep("r", 5), "l")) %>%
  kable_styling() %>%
  row_spec(c(2:5), bold = T)
```

```{r}
r_q2to23_first5 <- lmer(response ~ epi_ctry + (1 | epi_subj),
                        d_spex_base_q2to23,
                        contrasts = list(epi_ctry = contrasts_ctry_ctr))
```

```{r, include = F}
summary(r_q2to23_first5)$coefficients %>%
  data.frame() %>%
  rownames_to_column("parameter") %>%
  rename(b = Estimate, `standard error` = Std..Error, `t` = t.value,
         p = Pr...t..) %>%
  mutate_at(vars(-parameter, -p), funs(round(., 2))) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round(p, 3)),
         significant = ifelse(p < 0.05, "*", "")) %>%
  kable(align = c("l", rep("r", 5), "l")) %>%
  kable_styling() %>%
  row_spec(c(2:5), bold = T)
```

<P style="page-break-before: always">
# Spiritual experiences: Universal questions, set 1 (Questions #2-10)

## Overall scores

```{r}
d_spex_base_q2to10_scored_mb <- d_spex_base_q2to10_scored %>%
  group_by(epi_ctry) %>%
  multi_boot_standard("score") %>%
  ungroup()
```

```{r, fig.width = 4, fig.asp = 0.6, include = T}
spex_2to10_plot_a <- ggplot(d_spex_base_q2to10_scored,
                            aes(x = epi_ctry, y = score, color = epi_ctry)) +
  geom_hline(yintercept = 0*9, lty = 2, color = "black") +
  geom_hline(yintercept = 0.5*9, lty = 2, color = "black") +
  geom_hline(yintercept = 1*9, lty = 2, color = "black") +
  geom_jitter(height = 0.1, width = 0.4, alpha = 0.2, show.legend = F) +
  geom_pointrange(data = d_spex_base_q2to10_scored_mb,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 2, color = "black", show.legend = F) +
  geom_text(data = data.frame(x = 0.5,
                              y = c(0*9, 0.5*9, 1*9),
                              lab = c("~ All answers 'no'",
                                      "",
                                      # "~ All answers 'maybe'",
                                      "~ All answers 'yes'")),
            aes(x = x, y = y, label = lab),
            color = "black", hjust = 0, nudge_y = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 9, 1)) +
  labs(title = "Spiritual experiences (Questions #2-10)",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", y = "Score (range: 0-9)")

spex_2to10_plot_b <- ggplot(d_spex_base_q2to10_scored_mb,
                            aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  fatten = 4, show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 9, 1)) +
  labs(title = "Spiritual experiences (zoomed in)",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", y = "Score (range: 0-9)")

plot_grid(spex_2to10_plot_a, spex_2to10_plot_b, ncol = 2)
```

<P style="page-break-before: always">
## By item

```{r, fig.width = 6, fig.asp = 1, include = T}
d_spex_base_q2to10 %>%
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  ggplot(aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  facet_wrap(~ str_wrap(question_text, 50), ncol = 3) +
  facet_wrap(~ reorder(str_wrap(question_text, 60), order), ncol = 3) +
  geom_jitter(data = d_spex_base_q2to10, aes(y = response), 
              height = 0.05, alpha = 0.08, show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.5), 
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "Spiritual experiences #2-10: Responses to individual items",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", 
       y = "Mean response, i.e., proportion responding 'yes' (0 = no, 1 = yes)")
```


<P style="page-break-before: always">
# Spiritual experiences: Beings questions (Questions #11-15 + more for Thailand)

## Overall scores

### Considering all "beings" (more for Thailand)

```{r}
d_spex_base_q11to15_scored_propall_mb <- d_spex_base_q11to15_scored %>%
  group_by(epi_ctry) %>%
  multi_boot_standard("score_propall", na.rm = T) %>%
  ungroup()
```

```{r, fig.width = 4, fig.asp = 0.6, include = T}
spex_11to15_plot_a <- ggplot(d_spex_base_q11to15_scored,
                            aes(x = epi_ctry, y = score_propall, 
                                color = epi_ctry)) +
  geom_hline(yintercept = 0*1, lty = 2, color = "black") +
  geom_hline(yintercept = 0.5*1, lty = 2, color = "black") +
  geom_hline(yintercept = 1*1, lty = 2, color = "black") +
  geom_jitter(height = 0.02, width = 0.4, alpha = 0.2, show.legend = F) +
  geom_pointrange(data = d_spex_base_q11to15_scored_propall_mb,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 2, color = "black", show.legend = F) +
  geom_text(data = data.frame(x = 0.5,
                              y = c(0*1, 0.5*1, 1*1),
                              lab = c("~ All answers 'no'",
                                      "",
                                      # "~ All answers 'maybe'",
                                      "~ All answers 'yes'")),
            aes(x = x, y = y, label = lab),
            color = "black", hjust = 0, nudge_y = 0.05) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
  labs(title = "Spiritual experiences (Questions #11-15+)",
       subtitle = "Includes all beings for Thailand\nError bars are bootstrapped 95% CIs",
       x = "Site", y = "Proportion score (range: 0-1)")

spex_11to15_plot_b <- ggplot(d_spex_base_q11to15_scored_propall_mb,
                            aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  fatten = 4, show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
  labs(title = "Spiritual experiences (zoomed in)",
       subtitle = "Includes all beings for Thailand\nError bars are bootstrapped 95% CIs",
       x = "Site", y = "Proportion score (range: 0-1)")

plot_grid(spex_11to15_plot_a, spex_11to15_plot_b, ncol = 2)
```

<P style="page-break-before: always">
### Considering first five "beings" only

```{r}
d_spex_base_q11to15_scored_first5_mb <- d_spex_base_q11to15_scored %>%
  group_by(epi_ctry) %>%
  multi_boot_standard("score_first5", na.rm = T) %>%
  ungroup()
```

```{r, fig.width = 4, fig.asp = 0.6, include = T}
spex_11to15_plot_c <- ggplot(d_spex_base_q11to15_scored,
                            aes(x = epi_ctry, y = score_first5, 
                                color = epi_ctry)) +
  geom_hline(yintercept = 0*5, lty = 2, color = "black") +
  geom_hline(yintercept = 0.5*5, lty = 2, color = "black") +
  geom_hline(yintercept = 1*5, lty = 2, color = "black") +
  geom_jitter(height = 0.1, width = 0.4, alpha = 0.2, show.legend = F) +
  geom_pointrange(data = d_spex_base_q11to15_scored_first5_mb,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 2, color = "black", show.legend = F) +
  geom_text(data = data.frame(x = 0.5,
                              y = c(0*5, 0.5*5, 1*5),
                              lab = c("~ All answers 'no'",
                                      "",
                                      # "~ All answers 'maybe'",
                                      "~ All answers 'yes'")),
            aes(x = x, y = y, label = lab),
            color = "black", hjust = 0, nudge_y = 0.25) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 5, 1)) +
  labs(title = "Spiritual experiences (Questions #11-15+)",
       subtitle = "Includes first five beings for all sites\nError bars are bootstrapped 95% CIs",
       x = "Site", y = "Sum score (range: 0-5)")

spex_11to15_plot_d <- ggplot(d_spex_base_q11to15_scored_first5_mb,
                            aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  fatten = 4, show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 5, 1)) +
  labs(title = "Spiritual experiences (zoomed in)",
       subtitle = "Includes first five beings for all sites\nError bars are bootstrapped 95% CIs",
       x = "Site", y = "Sum score (range: 0-5)")

plot_grid(spex_11to15_plot_c, spex_11to15_plot_d, ncol = 2)
```

<P style="page-break-before: always">
## By item

```{r}
spex_11to15_plot_us <- d_spex_base_q11to15 %>%
  filter(epi_ctry == "US", grepl("usa", question)) %>%
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  ggplot(aes(x = epi_ctry, y = mean)) +
  facet_wrap(~ reorder(str_wrap(question_text, 40), order), ncol = 5) +
  geom_jitter(data = d_spex_base_q11to15 %>% 
                filter(epi_ctry == "US", grepl("usa", question)), 
              aes(y = response), 
              height = 0.05, alpha = 0.08, color = "#1b9e77", show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.5), 
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  labs(title = "US Spiritual experiences #11-15: Responses to individual items",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", 
       y = "Mean response (0 = no, 1 = yes)")
```

```{r}
spex_11to15_plot_gh <- d_spex_base_q11to15 %>%
  filter(epi_ctry == "Ghana", grepl("gha", question)) %>%
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  ggplot(aes(x = epi_ctry, y = mean)) +
  facet_wrap(~ reorder(str_wrap(question_text, 40), order), ncol = 5) +
  geom_jitter(data = d_spex_base_q11to15 %>% 
                filter(epi_ctry == "Ghana", grepl("gha", question)), 
              aes(y = response), 
              height = 0.05, alpha = 0.08, color = "#d95f02", show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.5), 
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  labs(title = "GHANA Spiritual experiences #11-15: Responses to individual items",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", 
       y = "Mean response (0 = no, 1 = yes)")
```

```{r}
spex_11to15_plot_th <- d_spex_base_q11to15 %>%
  filter(epi_ctry == "Thailand", grepl("thl", question)) %>%
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  ggplot(aes(x = epi_ctry, y = mean)) +
  facet_wrap(~ reorder(str_wrap(question_text, 40), order), ncol = 5) +
  geom_jitter(data = d_spex_base_q11to15 %>% 
                filter(epi_ctry == "Thailand", grepl("thl", question)), 
              aes(y = response), 
              height = 0.05, alpha = 0.08, color = "#7570b3", show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.5), 
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  labs(title = "THAILAND Spiritual experiences #11-15: Responses to individual items",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", 
       y = "Mean response (0 = no, 1 = yes)")
```

```{r}
spex_11to15_plot_ch <- d_spex_base_q11to15 %>%
  filter(epi_ctry == "China", grepl("chn", question)) %>%
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  ggplot(aes(x = epi_ctry, y = mean)) +
  facet_wrap(~ reorder(str_wrap(question_text, 40), order), ncol = 5) +
  geom_jitter(data = d_spex_base_q11to15 %>% 
                filter(epi_ctry == "China", grepl("chn", question)), 
              aes(y = response), 
              height = 0.05, alpha = 0.08, color = "#e7298a", show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.5), 
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  labs(title = "CHINA Spiritual experiences #11-15: Responses to individual items",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", 
       y = "Mean response (0 = no, 1 = yes)")
```

```{r}
spex_11to15_plot_vt <- d_spex_base_q11to15 %>%
  filter(epi_ctry == "Vanuatu", grepl("vut", question)) %>%
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  ggplot(aes(x = epi_ctry, y = mean)) +
  facet_wrap(~ reorder(str_wrap(question_text, 40), order), ncol = 5) +
  geom_jitter(data = d_spex_base_q11to15 %>% 
                filter(epi_ctry == "Vanuatu", grepl("vut", question)), 
              aes(y = response), 
              height = 0.05, alpha = 0.08, color = "#66a61e", show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.5), 
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  labs(title = "VANUATU Spiritual experiences #11-15: Responses to individual items",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", 
       y = "Mean response (0 = no, 1 = yes)")
```

```{r, fig.width = 6, fig.asp = 1.7}
plot_grid(spex_11to15_plot_us, spex_11to15_plot_gh, spex_11to15_plot_th,
          spex_11to15_plot_ch, spex_11to15_plot_vt, ncol = 1,
          rel_heights = c(1, 1, 2, 1, 1))
```

```{r, fig.width = 4, fig.asp = 2, include = T}
d_spex_base_q11to15 %>%
  group_by(epi_ctry, question, question_text, order) %>%
  multi_boot_standard("response", na.rm = T) %>%
  ungroup() %>% 
  filter(!is.na(mean), mean != "NaN") %>%
  ggplot(aes(x = reorder(str_wrap(question_text, 60), desc(order)), 
             y = mean, color = epi_ctry)) +
  facet_grid(epi_ctry ~ ., scales = "free", space = "free") +
  geom_jitter(data = d_spex_base_q11to15 %>% filter(!is.na(response)),
              aes(y = response),
              height = 0.05, alpha = 0.08, show.legend = F) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5),
                  color = "black", show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  labs(title = "Spiritual experiences #11-15:\nResponses to individual items",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Question", 
       y = "Mean response, i.e., proportion responding 'yes' (0 = no, 1 = yes)") +
  coord_flip()
```


<P style="page-break-before: always">
# Spiritual experiences: Universal questions, set 2 (Questions #16-21)

## Overall scores

```{r}
d_spex_base_q16to21_scored_mb <- d_spex_base_q16to21_scored %>%
  group_by(epi_ctry) %>%
  multi_boot_standard("score") %>%
  ungroup()
```

```{r, fig.width = 4, fig.asp = 0.6, include = T}
spex_q16to21_plot_a <- ggplot(d_spex_base_q16to21_scored,
                            aes(x = epi_ctry, y = score, color = epi_ctry)) +
  geom_hline(yintercept = 0*6, lty = 2, color = "black") +
  geom_hline(yintercept = 0.5*6, lty = 2, color = "black") +
  geom_hline(yintercept = 1*6, lty = 2, color = "black") +
  geom_jitter(height = 0.2, width = 0.4, alpha = 0.2, show.legend = F) +
  geom_pointrange(data = d_spex_base_q16to21_scored_mb,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 2, color = "black", show.legend = F) +
  geom_text(data = data.frame(x = 0.5,
                              y = c(0*6, 0.5*6, 1*6),
                              lab = c("~ All answers 'no'",
                                      "",
                                      # "~ All answers 'maybe'",
                                      "~ All answers 'yes'")),
            aes(x = x, y = y, label = lab),
            color = "black", hjust = 0, nudge_y = 0.25) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 6, 1)) +
  labs(title = "Spiritual experiences (Questions #16-21)",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", y = "Score (range: 0-6)")

spex_q16to21_plot_b <- ggplot(d_spex_base_q16to21_scored_mb,
                            aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  fatten = 4, show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 6, 1)) +
  labs(title = "Spiritual experiences (zoomed in)",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", y = "Score (range: 0-6)")

plot_grid(spex_q16to21_plot_a, spex_q16to21_plot_b, ncol = 2)
```

<P style="page-break-before: always">
## By item

[not yet done]


<P style="page-break-before: always">
# Spiritual experiences: Universal questions, set 3 (Questions #22-23)

## Overall scores

```{r}
d_spex_base_q22to23_scored_mb <- d_spex_base_q22to23_scored %>%
  group_by(epi_ctry) %>%
  multi_boot_standard("score") %>%
  ungroup()
```

```{r, fig.width = 4, fig.asp = 0.6, include = T}
spex_q22to23_plot_a <- ggplot(d_spex_base_q22to23_scored,
                            aes(x = epi_ctry, y = score, color = epi_ctry)) +
  geom_hline(yintercept = 0*2, lty = 2, color = "black") +
  geom_hline(yintercept = 0.5*2, lty = 2, color = "black") +
  geom_hline(yintercept = 1*2, lty = 2, color = "black") +
  geom_jitter(height = 0.2, width = 0.4, alpha = 0.2, show.legend = F) +
  geom_pointrange(data = d_spex_base_q22to23_scored_mb,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  fatten = 2, color = "black", show.legend = F) +
  geom_text(data = data.frame(x = 0.5,
                              y = c(0*2, 0.5*2, 1*2),
                              lab = c("~ All answers 'no'",
                                      "",
                                      # "~ All answers 'maybe'",
                                      "~ All answers 'yes'")),
            aes(x = x, y = y, label = lab),
            color = "black", hjust = 0, nudge_y = 0.1) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 2, 1)) +
  labs(title = "Spiritual experiences (Questions #22-23)",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", y = "Score (range: 0-2)")

spex_q22to23_plot_b <- ggplot(d_spex_base_q22to23_scored_mb,
                            aes(x = epi_ctry, y = mean, color = epi_ctry)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  fatten = 4, show.legend = F) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(breaks = seq(0, 2, 1)) +
  labs(title = "Spiritual experiences (zoomed in)",
       subtitle = "Error bars are bootstrapped 95% CIs",
       x = "Site", y = "Score (range: 0-2)")

plot_grid(spex_q22to23_plot_a, spex_q22to23_plot_b, ncol = 2)
```

<P style="page-break-before: always">
## By item

[not yet done]


<P style="page-break-before: always">
# Relationships between porosity and spiritual experience

## Considering all "beings" (more for Thailand)

```{r}
d_por_spex_base_q2to23_propall <- d_spex_base_q2to23_scored_propall %>% 
  rename(spex_score_propall = score) %>%
  full_join(d_por_scored %>% rename(por_score = score)) %>%
  group_by(epi_ctry) %>%
  mutate(por_score_std = scale(por_score),
         spex_score_propall_std = scale(spex_score_propall)) %>%
  ungroup()

# effect-code by default
contrasts(d_por_spex_base_q2to23_propall$epi_ctry) <- contr.sum(5)
```

```{r, fig.width = 4, fig.asp = 0.35, include = F}
ggplot(d_por_spex_base_q2to23_propall,
       aes(x = por_score, y = spex_score_propall, color = epi_ctry)) +
  facet_grid(~ epi_ctry) +
  geom_point(alpha = 0.2, show.legend = F) +
  geom_smooth(method = "lm", color = "black", show.legend = F) +
  scale_x_continuous(breaks = seq(0, 16, 4)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  scale_color_brewer(palette = "Dark2") +
  labs(title = "Relationship between porosity and spiritual experience",
       subtitle = "Includes all beings for Thailand",
       x = "Porosity score (0-16)",
       y = "Spiritual experience\nproportion score (0-1)")
```

```{r, fig.width = 4, fig.asp = 0.3, include = T}
ggplot(d_por_spex_base_q2to23_propall,
       aes(x = por_score_std, y = spex_score_propall_std, color = epi_ctry)) +
  facet_wrap(~ epi_ctry, ncol = 5, scales = "free") +
  geom_point(alpha = 0.2, show.legend = F) +
  geom_smooth(method = "lm", color = "black", show.legend = F) +
  # scale_x_continuous(breaks = seq(0, 16, 4)) +
  # scale_y_continuous(breaks = seq(0, 22, 4)) +
  scale_color_brewer(palette = "Dark2") +
    labs(title = "Relationship between porosity and spiritual experience",
       subtitle = "Includes all beings for Thailand",
       x = "Porosity score (standardized within each site)",
       y = "Spiritual exp. proportion score\n(standardized within each site)")
```

```{r, fig.width = 4, fig.asp = 0.35, include = F}
ggplot(d_por_spex_base_q2to23_propall %>%
         filter(abs(por_score_std) < 2,
                abs(spex_score_propall_std) < 2),
       aes(x = por_score_std, y = spex_score_propall_std, color = epi_ctry)) +
  facet_wrap(~ epi_ctry, ncol = 5) +
  geom_point(alpha = 0.2, show.legend = F) +
  geom_smooth(method = "lm", color = "black", show.legend = F) +
  # scale_x_continuous(breaks = seq(0, 16, 4)) +
  # scale_y_continuous(breaks = seq(0, 22, 4)) +
  scale_color_brewer(palette = "Dark2") +
  labs(title = "Relationship between porosity and spiritual experience",
       subtitle = "Includes all beings for Thailand\nExcluding outliers (z > 2 or z < -2)",
       x = "Porosity score (standardized within each site)",
       y = "Spiritual exp. proportion score\n(standardized within each site)")
```

```{r}
r_por_spex_propall <- lm(por_score_std ~ spex_score_propall_std * epi_ctry,
                        d_por_spex_base_q2to23_propall,
                        contrasts = list(epi_ctry = contrasts_ctry_ctr))
```

```{r, include = T}
summary(r_por_spex_propall)$coefficients %>%
  data.frame() %>%
  rownames_to_column("parameter") %>%
  rename(b = Estimate, `standard error` = Std..Error, `t` = t.value,
         p = Pr...t..) %>%
  mutate_at(vars(-parameter, -p), funs(round(., 2))) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round(p, 3)),
         significant = ifelse(p < 0.05, "*", "")) %>%
  kable(align = c("l", rep("r", 5), "l")) %>%
  kable_styling() %>%
  row_spec(c(2, 7:10), bold = T)
```

```{r}
r_por_spex_propall_us <- lm(por_score_std ~ spex_score_propall_std,
                           d_por_spex_base_q2to23_propall %>%
                             filter(epi_ctry == "US"))

r_por_spex_propall_gh <- lm(por_score_std ~ spex_score_propall_std,
                           d_por_spex_base_q2to23_propall %>%
                             filter(epi_ctry == "Ghana"))

r_por_spex_propall_th <- lm(por_score_std ~ spex_score_propall_std,
                           d_por_spex_base_q2to23_propall %>%
                             filter(epi_ctry == "Thailand"))

r_por_spex_propall_ch <- lm(por_score_std ~ spex_score_propall_std,
                           d_por_spex_base_q2to23_propall %>%
                             filter(epi_ctry == "China"))

r_por_spex_propall_vt <- lm(por_score_std ~ spex_score_propall_std,
                           d_por_spex_base_q2to23_propall %>%
                             filter(epi_ctry == "Vanuatu"))
```

```{r, include = T}
rbind(summary(r_por_spex_propall_us)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "US"),
      summary(r_por_spex_propall_gh)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "Ghana"),
      summary(r_por_spex_propall_th)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "Thailand"),
      summary(r_por_spex_propall_ch)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "China"),
      summary(r_por_spex_propall_vt)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "Vanuatu")) %>%
  rename(b = Estimate, `standard error` = Std..Error, `t` = t.value,
         p = Pr...t..) %>%
  mutate_at(vars(-c(parameter, p, site)), funs(round(., 2))) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round(p, 3)),
         significant = ifelse(p < 0.05, "*", "")) %>%
  select(-site) %>%
  kable(align = c("l", rep("r", 5), "l")) %>%
  kable_styling() %>%
  group_rows("US", 1, 2) %>%
  group_rows("Ghana", 3, 4) %>%
  group_rows("Thailand", 5, 6) %>%
  group_rows("China", 7, 8) %>%
  group_rows("Vanuatu", 9, 10) %>%
  row_spec(c(seq(2, 10, 2)), bold = T)
```

<P style="page-break-before: always">
## Considering first five "beings" only

```{r}
d_por_spex_base_q2to23_first5 <- d_spex_base_q2to23_scored_first5 %>% 
  rename(spex_score_first5 = score) %>%
  full_join(d_por_scored %>% rename(por_score = score)) %>%
  group_by(epi_ctry) %>%
  mutate(por_score_std = scale(por_score),
         spex_score_first5_std = scale(spex_score_first5)) %>%
  ungroup()

# effect-code by default
contrasts(d_por_spex_base_q2to23_propall$epi_ctry) <- contr.sum(5)
```

```{r, fig.width = 4, fig.asp = 0.35, include = F}
ggplot(d_por_spex_base_q2to23_first5,
       aes(x = por_score, y = spex_score_first5, color = epi_ctry)) +
  facet_grid(~ epi_ctry) +
  geom_point(alpha = 0.2, show.legend = F) +
  geom_smooth(method = "lm", color = "black", show.legend = F) +
  scale_x_continuous(breaks = seq(0, 16, 4)) +
  scale_y_continuous(breaks = seq(0, 22, 4)) +
  scale_color_brewer(palette = "Dark2") +
  labs(title = "Relationship between porosity and spiritual experience",
       subtitle = "Includes first five beings for all sites",
       x = "Porosity score (0-16)",
       y = "Spiritual experience\nsum score (0-22)")
```

```{r, fig.width = 4, fig.asp = 0.3, include = T}
ggplot(d_por_spex_base_q2to23_first5,
       aes(x = por_score_std, y = spex_score_first5_std, color = epi_ctry)) +
  facet_wrap(~ epi_ctry, ncol = 5, scales = "free") +
  geom_point(alpha = 0.2, show.legend = F) +
  geom_smooth(method = "lm", color = "black", show.legend = F) +
  # scale_x_continuous(breaks = seq(0, 16, 4)) +
  # scale_y_continuous(breaks = seq(0, 22, 4)) +
  scale_color_brewer(palette = "Dark2") +
  labs(title = "Relationship between porosity and spiritual experience",
       subtitle = "Includes first five beings for all sites",
       x = "Porosity score (standardized within each site)",
       y = "Spiritual experience sum score\n(standardized within each site)")
```

```{r, fig.width = 4, fig.asp = 0.35, include = F}
ggplot(d_por_spex_base_q2to23_first5 %>%
         filter(abs(por_score_std) < 2,
                abs(spex_score_first5_std) < 2),
       aes(x = por_score_std, y = spex_score_first5_std, color = epi_ctry)) +
  facet_wrap(~ epi_ctry, ncol = 5) +
  geom_point(alpha = 0.2, show.legend = F) +
  geom_smooth(method = "lm", color = "black", show.legend = F) +
  # scale_x_continuous(breaks = seq(0, 16, 4)) +
  # scale_y_continuous(breaks = seq(0, 22, 4)) +
  scale_color_brewer(palette = "Dark2") +
  labs(title = "Relationship between porosity and spiritual experience",
       subtitle = "Includes first five beings for all sites\nExcluding outliers (z > 2 or z < -2)",
       x = "Porosity score (standardized within each site)",
       y = "Spiritual experience sum score\n(standardized within each site)")
```

```{r}
r_por_spex_first5 <- lm(por_score_std ~ spex_score_first5_std * epi_ctry,
                        d_por_spex_base_q2to23_first5,
                        contrasts = list(epi_ctry = contrasts_ctry_ctr))
```

```{r, include = T}
summary(r_por_spex_first5)$coefficients %>%
  data.frame() %>%
  rownames_to_column("parameter") %>%
  rename(b = Estimate, `standard error` = Std..Error, `t` = t.value,
         p = Pr...t..) %>%
  mutate_at(vars(-parameter, -p), funs(round(., 2))) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round(p, 3)),
         significant = ifelse(p < 0.05, "*", "")) %>%
  kable(align = c("l", rep("r", 5), "l")) %>%
  kable_styling() %>%
  row_spec(c(2, 7:10), bold = T)
```

```{r}
r_por_spex_first5_us <- lm(por_score_std ~ spex_score_first5_std,
                           d_por_spex_base_q2to23_first5 %>%
                             filter(epi_ctry == "US"))

r_por_spex_first5_gh <- lm(por_score_std ~ spex_score_first5_std,
                           d_por_spex_base_q2to23_first5 %>%
                             filter(epi_ctry == "Ghana"))

r_por_spex_first5_th <- lm(por_score_std ~ spex_score_first5_std,
                           d_por_spex_base_q2to23_first5 %>%
                             filter(epi_ctry == "Thailand"))

r_por_spex_first5_ch <- lm(por_score_std ~ spex_score_first5_std,
                           d_por_spex_base_q2to23_first5 %>%
                             filter(epi_ctry == "China"))

r_por_spex_first5_vt <- lm(por_score_std ~ spex_score_first5_std,
                           d_por_spex_base_q2to23_first5 %>%
                             filter(epi_ctry == "Vanuatu"))
```

```{r, include = T}
rbind(summary(r_por_spex_first5_us)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "US"),
      summary(r_por_spex_first5_gh)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "Ghana"),
      summary(r_por_spex_first5_th)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "Thailand"),
      summary(r_por_spex_first5_ch)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "China"),
      summary(r_por_spex_first5_vt)$coefficients %>%
        data.frame() %>%
        rownames_to_column("parameter") %>%
        mutate(site = "Vanuatu")) %>%
  rename(b = Estimate, `standard error` = Std..Error, `t` = t.value,
         p = Pr...t..) %>%
  mutate_at(vars(-c(parameter, p, site)), funs(round(., 2))) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round(p, 3)),
         significant = ifelse(p < 0.05, "*", "")) %>%
  select(-site) %>%
  kable(align = c("l", rep("r", 5), "l")) %>%
  kable_styling() %>%
  group_rows("US", 1, 2) %>%
  group_rows("Ghana", 3, 4) %>%
  group_rows("Thailand", 5, 6) %>%
  group_rows("China", 7, 8) %>%
  group_rows("Vanuatu", 9, 10) %>%
  row_spec(c(seq(2, 10, 2)), bold = T)
```
